%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Quizaufgaben

\begin{quiz}
\quizAufgabe{%
The sets of nogoods $\Delta_\Pi$ and $\Lambda_\Pi$ are the 
input of the (deterministic) propagation inside
\textsf{CDNL-ASP($\Pi$)}.
}
\quizAufgabe{%
If a normal program~$\Pi$ is ``tight'', 
then the sets of nogoods 
$\Delta_\Pi$ and $\Delta_\Pi\cup\Lambda_\Pi$ 
have the same solutions.%
}
\quizAufgabe{%
If a normal program~$\Pi$ has no stable models, 
then the nogoods in 
$\Delta_\Pi\cup\Lambda_\Pi$
imply the empty nogood
$\emptyset$.%
}
\quizAufgabe{%
If a normal program~$\Pi$ has no stable models, 
then \textsf{CDNL-ASP($\Pi$)}
is not guaranteed to terminate.% 
}
\quizAufgabe{%
If the dynamic nogoods that are not ``asserting''
(ie., those that do not imply any literal of the current assignment)
are removed from~$\nabla$, 
then \textsf{CDNL-ASP($\Pi$)}
is not guaranteed to terminate.% 
}
% \quizAufgabe{%
% Für ein gegebenes normales Programm~$\Pi$ generiert 
% \textsf{CDNL-ASP($\Pi$)} die Menge
% $\Delta_\Pi\cup\Lambda_\Pi$ von Nogoods.}
% \quizAufgabe{%
% Nach der Behandlung eines Konflikts wird innerhalb von
% \textsf{CDNL-ASP}
% nicht notwendigerweise das letzte (heuristisch bestimmte)
% Entscheidungsliteral gedreht.}
%\quizAufgabe[true]{A Unique Implication Point (UIP) of a decision level
%             along with literals assigned at smaller decision levels
%             lead to a conflict by propagation.}
%\quizAufgabe[true]{Each decision level beyond~$0$ at which a conflict occurs has
%             some UIP.}
\end{quiz}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Lösungen

\begin{Loesung}
\begin{quizLoesung}
\quizAufgabe[false]{%
The (deterministic) propagation within 
\textsf{CDNL-ASP($\Pi$)}
is based on the completion nogoods in~$\Delta_\Pi$.
The loop nogoods  
in~$\Lambda_\Pi$
are determined and recorded on demand, 
when they are needed to falsify an unfounded set~$U$. 
}
\quizAufgabe[true]{%
In general, the solutions of $\Delta_P\cup\Lambda_P$ correspond to the stable models of $P$,
and the solutions of $\Delta_P$ correspond to the supported models of $P$.
If $P$ is ``tight'', then the stable models and the supported models of $P$ coincide.
Hence, in this case the solutions of $\Delta_P$ and $\Delta_P\cup\Lambda_P$ are the same.
}
\quizAufgabe[true]{%
If $\Pi$ has no stable models, 
then
$\Delta_\Pi\cup\Lambda_\Pi$ has no solutions.
That means that every set of literals is a nogood 
(because it does not hold in any solution).
This holds in particular for the empty nogood $\emptyset$.%
}
\quizAufgabe[false]{%
For every conflict at a decision level~$\mathit{dl}>0$,
a nogood~$\delta$, 
that implies (at least) one literal at decision level~$k<\mathit{dl}$,
is added to the set $\nabla$ of dynamic nogoods.
After backjumping to~$k$,
the number of assigned literals at~$k$ is increased.
Given that the number of literals is finite, 
at decision level~$k$ it is not possible to assign an arbitrary number of literals, 
so sooner or later a conflict at~$k$ 
(or at a decision level $\mathit{dl}<k$) must occur. 
This holds, in particular, at decision level~$0$, where a conflict indicates
the absence of stable models.%
}
\quizAufgabe[false]{%
The argument of the previous quiz task applies also here, 
for the case where (after backjumping) some nogoods~$\delta$, 
that do not imply any literal of the current assignment, 
are removed from~$\nabla$.
Note that a nogood~$\delta$ determined in the conflict analysis
is ``asserting'' after the backjump to a decision level~$k$, 
so it must be kept in~$\nabla$ until the decision level~$k$ is 
taken back (by another backjump).
}
%\quizAufgabe[true]{A Unique Implication Point (UIP) of a decision level
%             along with literals assigned at smaller decision levels
%             lead to a conflict by propagation.}
%\quizAufgabe[true]{Each decision level beyond~$0$ at which a conflict occurs has
%             some UIP.}
\end{quizLoesung}
\newpage
\end{Loesung}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "uebung08"
%%% End: 
